### 2024-10-20 src/Submission.Rnw
Changed to ddat

# Calculate the correlation between each predictor and the target
correlations <- sapply(predictor_vars, function(var) {
  cor(diabetes[[var]], diabetes$target)
})

>>>>

# Calculate the correlation between each predictor and the target
correlations <- sapply(predictor_vars, function(var) {
  cor(ddat[[var]], ddat$target)
})
